Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
Missed this small edit

\paragraph*{Malacology:} Malacology exposes Ceph's PAXOS-based monitoring 
service in two ways. First, a Lua VM is embedded in the monitors that implements 
a generic API for creating maps and associating arbitrary data to them. This API 
also allows clients to specify small snippets of Lua code that can be executed 
on monitors. As a consequence of this, applications can define simple but useful 
domain-specific logic to the PAXOS quorum, such as authorization control (just 
specific clients can write new values) or to trigger actions based on specific 
values (e.g. sanitize values). Since the monitor is intended to be out of 
high-performance I/O paths, a general guideline is to make use of this 
functionality infrequently and to assign small values to maps. Malacology itself 
makes use of this functionality to version object interfaces defined in OSDs 
(\S\ref{active-storage}) and load balancing policies in MDSs 
(\S\ref{malacology:mds}).

>>>>

\paragraph*{Malacology:} Malacology exposes Ceph's PAXOS-based monitoring 
service by embedding a Lua VM in the monitors that implements a generic API for 
creating maps and associating arbitrary data to them. This API also allows 
clients to specify small snippets of Lua code that can be executed on monitors. 
As a consequence of this, applications can define simple but useful 
domain-specific logic to the PAXOS quorum, such as authorization control (just 
specific clients can write new values) or to trigger actions based on specific 
values (e.g. sanitize values). Since the monitor is intended to be out of 
high-performance I/O paths, a general guideline is to make use of this 
functionality infrequently and to assign small values to maps. Malacology itself 
makes use of this functionality to version object interfaces defined in OSDs 
(\S\ref{active-storage}) and load balancing policies in MDSs 
(\S\ref{malacology:mds}).
